DNSKEY Management

### 2012-12-07 paper/paper.tex
Minor English fixes

This is achieved by establishing a trust chain between something known and the domain that is being queried: e.g., I trust this person to tell me the truth and to be who it claims to be, because a friend I trust is trusting this person.

@@

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch.|'s public key ;
\item Check \verb|lacal.epfl.ch.|'s public key authenticity by obtaining its signature from \verb|epfl.ch.|'s DNS server ;
\item Verify the query -- containing \verb|lacal.epfl.ch.|'s public key signature -- returned by \verb|epfl.ch.| with its public key;
\item Check \verb|epfl.ch.|'s public key against the corresponding signature served by \verb|ch.|;
\item Again, verify \verb|ch.|'s responses by getting its public key signature from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

While standard DNS can perfectly live with some of the temporary imprecisions generated by non-optimal interactions between the three R's, DNSSEC is far less tolerant to such jitter: typically, if the \verb|epfl.ch.| zone updates its keys but SWITCH fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch.|'s DNS servers will appear as illegitimate whereas they perfectly are, and this will last as long as SWITCH's servers do not reflect the update.

@@

In both cases,  this \emph{transfer} scenario will require a certain level of cooperation between two concurrent companies.

>>>>

This is achieved by establishing a trust chain between something known and the domain that is being queried: e.g., I trust this person to tell me the truth and to be who it claims to be, because a friend I trust trusts this person.

@@

\begin{enumerate}
\item Verify the reply's authenticity using \verb|lacal.epfl.ch.|'s
  public key;
\item Check the authenticity of \verb|lacal.epfl.ch.|'s public key by
  obtaining its signature from \verb|epfl.ch.|'s DNS server;
\item Verify the query -- containing \verb|lacal.epfl.ch.|'s public key signature -- returned by \verb|epfl.ch.| with its public key;
\item Check \verb|epfl.ch.|'s public key against the corresponding signature served by \verb|ch.|;
\item Again, verify \verb|ch.|'s responses by getting its public key signature from the root domain.
\item Finally, the root domain's responses can be verified with its already known public key.
\end{enumerate}

@@

While standard DNS can perfectly live with some of the temporary imprecisions caused by non-optimal interactions between the three R's, DNSSEC is far less tolerant to such jitter: typically, if the \verb|epfl.ch.| zone updates its keys but SWITCH fails to reflect this change fast enough in its records, query responses from \verb|epfl.ch.|'s DNS servers will appear as illegitimate whereas they perfectly are, and this will last as long as SWITCH's servers do not reflect the update.

@@

In both cases,  this \emph{transfer} scenario will require a certain level of cooperation between two competing companies.
